Supplementary Materials from: \textit{Innovation and elaboration on the avian tree of life}; Science Advances, in review

### 2023-08-21 Manuscript/reponse_letter.tex
Update reponse_letter.tex

\begin{itemize}
    \item We now clearly distinguish the two types of elaboration and innovation: $elaboration_{species}$ and $innovation_{species}$ that focuses on the macro-evolutionary scale and $elaboration_{clades}$ and $innovation_{clades}$ that focuses on the mega-evolutionary scale;
    \item For the analyses on elaboration and innovation at the macro scale ($elaboration_{species}$ and $innovation_{species}$), we now only focus on the projection of species onto their order’s major axes;
    \item We added two new figures and a table in the main text: the cheat sheet figure (previously in the supplementaries, now in the introduction), the correlation figure and a table from the new PGLS results; 
    \item We have added several new analyses to the supplementary materials including: correlations between elaboration/innovation, elaboration and innovation through time and random skewers analysis;
    \item We have linked our metrics definitions to previous work in the supplementary materials;
    \item We have made the vocabulary more consistent throughout the manuscript;
    \item We fully rewrote the introduction and most of the results/discussion section.
\end{itemize}

We fully describe each change below.
\bigskip
Best regards,
\bigskip
Thomas Guillerme, on behalf of all co-authors.

@@

>>>>

\begin{itemize}
    \item We now clearly distinguish the two types of elaboration and innovation: $elaboration_{species}$ and $innovation_{species}$ that focuses on the macro-evolutionary scale and $elaboration_{clades}$ and $innovation_{clades}$ that focuses on the mega-evolutionary scale;
    \item For the analyses on elaboration and innovation at the macro scale ($elaboration_{species}$ and $innovation_{species}$), we now only focus on the projection of species onto their order’s major axes;
    \item We added two new figures and a table in the main text: the cheat sheet figure (previously in the supplementaries, now in the introduction), the correlation figure and a table from the new PGLS results and revamped all the previous figures.
    \item We have added several new analyses to the supplementary materials including: correlations between elaboration/innovation, elaboration and innovation through time and random skewers analysis;
    \item We have linked our metrics definitions to previous work in the supplementary materials;
    \item We have made the vocabulary more consistent throughout the manuscript;
    \item We fully rewrote the introduction and most of the results/discussion section.
\end{itemize}

\noindent We fully describe each change below.

\bigskip

\noindent Best regards,

\bigskip

\noindent Thomas Guillerme, on behalf of all co-authors.

@@

We now reflect that in the supplementary materials section 4.5:

\noindent\textit{In \cite{hansen2008measuring}, the inverse of \textbf{G} is defined as ``the fraction of the genetic variation that is independent of potentially constraining characters'' which in our case will be harder to define.
Although it would technically be possible to use the inverse of the \textbf{R} matrix used here ($VCV_{clade}$), it is unclear what it would represent biologically.}
